\chapter{Regression}\label{code:regression}

In this appendix you can find the code for a linear regression implementation using \emph{sklearn}, as well as some examples of SVMs used for regression.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/LinearRegression/Regression.py}

\chapter{Manual Regression}\label{code:manualregression}
In this appendix you find a linear regression algorithm build from the ground up.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/LinearRegression/ManualRegression.py}

\chapter{K Nearest Neighbors}\label{code:knn}
In this appendix you can find the code for a K nearest neighbors implementation using \emph{sklearn}.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/KNearestNeighbors/KNearestNeighbors.py}

\chapter{Manual K Nearest Neighbors}\label{code:mknn}
In this appendix you find a linear K nearest neighbors build from the ground up.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/KNearestNeighbors/ManualKNearestNeighbors.py}

\chapter{Support Vector Machine}\label{code:svm}
In this appendix you can find the code for a Support Vector Machine implementation using \emph{sklearn}.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/SVM/SVM.py}

\chapter{Manual Support Vector Machine}\label{code:msvm}
In this appendix you find a Support Vector Machine build from the ground up.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/SVM/ManualSVM.py}

\chapter{K-Means}\label{code:kmeans}
In this appendix you find the use of \emph{scikit}'s K-Means classifier for simple data.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/KMeans/k-means.py}

\chapter{Nonnumerical K-Means}\label{code:nonnumerical-kmeans}
In this appendix you find the use of \emph{scikit}'s K-Means classifier for nonnumerical data.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/KMeans/nonnumerical-k-means.py}

\chapter{Manual K-Means}\label{code:manual-kmeans}
In this appendix you find the implementation of a K-Means classifier from the ground up.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/KMeans/manual-k-means.py}

\chapter{Mean Shift}\label{code:meanshift}
In this appendix you find the use of \emph{scikit}'s Mean Shift classifier for simple data.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/MeanShift/mean-shift.py}

\chapter{Nonnumerical Mean Shift}\label{code:nonnumerical-meanshift}
In this appendix you find the use of \emph{scikit}'s Mean Shift classifier for nonnumerical data.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/MeanShift/nonnumerical-mean-shift.py}

\chapter{Manual Mean Shift}\label{code:manual-meanshift}
In this appendix you find the implementation of a Mean Shift classifier from the ground up.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/MeanShift/manual-mean-shift.py}

\chapter{Create Sentiment Featureset}\label{code:create-sentiment-featureset}
In this appendix you find the implementation for creating a sentiment featureset.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/create_sentiment_featuresets.py}

\chapter{Convolutional Neural Network}\label{code:cnn}
In this appendix you find the implementation of a convolutional neural network using TensorFlow.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tensorflow-cnn.py}

\chapter{Neural Network Example}\label{code:nn-example}
In this appendix you find the implementation of a simple example of a Neural Network using TensorFlow.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tensorflow-example.py}

\chapter{Long Short Term Menomory}\label{code:ltsm}
In this appendix you find the implementation of a LTSM using TensorFlow.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tensorflow-ltsm.py}

\chapter{Number Recognition using Neural Nets}\label{code:number-recognition}
In this appendix you find the implementation of a neural network using TensorFlow to implement a number recognition program.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tensorflow-numberrecognition.py}

\chapter{Sentiment Analyses with Neural Nets}\label{code:sentiment}
In this appendix you find the implementation of a sentiment analyses using Neural Networks from TensorFlow.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tensorflow-sentiment.py}

\chapter{Convolution with TFLearn}\label{code:tflearn}
In this appendix you find the implementation of a convolutional neural net using TFLearn.
\lstinputlisting[language=Python]{/home/tom/Dropbox/Workspace/Python/PracticalML/NeuralNetwork/tflearn-convolution.py}
%TODO some code falls out of the page, fix this